# Body

Some text


::: {.callout-note icon=false}

## A callout note with custom headline

Some text here some text here 
Some text here some text here 
Some text here some text here 
Some text here some text here 
Some text here some text here 


:::


> Blockquote Blockquote Blockquote Blockquote 
Blockquote Blockquote Blockquote Blockquote 
Blockquote Blockquote Blockquote 

Some text


| Line Block
|   Spaces and newlines
|   are preserved

Some text

::: {.callout-note icon=false}

## A callout note with custom headline and blockquote

Some text here some text here 
Some text here some text here

> Blockquote Blockquote Blockquote Blockquote 
Blockquote Blockquote Blockquote Blockquote 
Blockquote Blockquote Blockquote 

Some text here some text here

| Line Block
|   Spaces and newlines
|
|   are preserved

Some text here some text here 
Some text here some text here 

:::


::: {.callout-note icon=false}

## Another callout note with custom headline and blockquote

Some text here some text here 
Some text here some text here

> Blockquote Blockquote Blockquote Blockquote 
Blockquote Blockquote Blockquote Blockquote 
Blockquote Blockquote Blockquote

|
|   Some text here some text here Some text here some text here Some text here some text here Some text here some text here Some text here some text here 
Some text here some text here Some text here some text here Some text here some text here Some text here some text here 

:::


## Headline level 2

Some text here some text here 
Some text here some text here 

### Headline level 3

Some text here some text here 
Some text here some text here 

#### Headline level 4

Some text here some text here 
Some text here some text here 


## Try tables


### Conditional table formatting.


```{r table prep html}
#| eval: !expr knitr::is_html_output()

# this is possible (chunk level)
.format = "html"
.bootstrap_options = c("condensed", "hover")
.col_width = "170px" 

```


```{r table html}

data_path = "../../data/"
testdata <- get(load(data_path |> paste0(x = _, "mtcars.Rda")))


# or within chunks

.format = if (knitr::is_html_output()) {
  "html"
} else {
    "latex"
  }
.bootstrap_options = if (knitr::is_html_output()) {
  c("condensed", "hover")
} else {
    "basic"
  }
.col_width = if (knitr::is_html_output()) {
  "170px"
  } else {
    "70pt"
  }
.booktabs = if (knitr::is_html_output()) {
  FALSE
} else {
  TRUE
}
.longtable = if (knitr::is_html_output()) {
  FALSE
} else {
  TRUE
}
.font_size = 10

knitr::kable(
  x = testdata,
  format = .format,
  escape = FALSE,
  booktabs = .booktabs,
  longtable = .longtable,
  table.attr = 'data-quarto-disable-processing="true"' # if quarto HERE
) |>
  kableExtra::kable_styling(
    bootstrap_options = .bootstrap_options, 
    latex_options = "basic",
    full_width = FALSE,
    position = "left",
    font_size = .font_size
  ) |> 
  kableExtra::column_spec(
    column = 2:ncol(testdata),
    width = .col_width
  ) |>
  kableExtra::collapse_rows(
    columns = seq_along(colnames(testdata)),
    valign = "middle"
  ) 

```



